Extended Data

### 2022-03-13 doc/manuscript/Dow_manuscript_Nature.Rmd
consistently use "Harvard Forest" as opposed to HF

In contrast to the pronounced effects of CTW $T_{max}$ on the timing of growth, its effects on $g_{max}$ and $\Delta DBH$ were weak and inconsistent (Figs. `r schematic_summary`, `r EDF_pheno_all`). 
Specifically, $g_{max}$, which occurred very close to $DOY_{50}$, displayed extremely small negative changes (HF) or changes in opposite directions (SCBI) in relationship to CTW $T_{max}$ for ring- and diffuse- porous species.
$\Delta DBH$ displayed a weak positive relationship (+0.029-0.08 mm/ $^\circ$C) with CTW $T_{max}$ at SCBI and a weak negative relationship (-0.2-0.03mm/ $^\circ$C) at HF (`r EDF_pheno_Tmax_climwin`).

@@

The raw dendrometer band data were manually inspected before analysis. 
We screened the data for three classes of errors. 
First, when a measurement was drastically different from previous and following measurements, it was assumed to be a human error and removed.
Second, when measurements remained essentially unchanged for several readings, followed by a sudden jump then return to a normal growth pattern, this was assumed to be a case where the band was stuck on the tree bark and then released. 
In these cases, the full annual record for the tree was removed.
Third, data points that deviated substantially from normal growth patterns, but for unknown causes, were removed. 
If a majority of the data points fell into this class within a tree-year, the entire year was removed from the analysis.
We also removed tree-years with small or negligible total growth ($\Delta DBH$ $\le 0.05$ mm; SCBI = 26, Harvard Forest = 253), and tree-years where first intraannual measurement was later than the first spring survey (trees that were missed in the initial census; SCBI = 22, HF = 8).
These were removed because they reduce the reliability of predicted growth in the modeled curves.

>>>>

In contrast to the pronounced effects of CTW $T_{max}$ on the timing of growth, its effects on $g_{max}$ and $\Delta DBH$ were weak and inconsistent (Figs. `r schematic_summary`, `r EDF_pheno_all`). 
Specifically, $g_{max}$, which occurred very close to $DOY_{50}$, displayed extremely small negative changes (Harvard Forest) or changes in opposite directions (SCBI) in relationship to CTW $T_{max}$ for ring- and diffuse- porous species.
$\Delta DBH$ displayed a weak positive relationship (+0.029-0.08 mm/ $^\circ$C) with CTW $T_{max}$ at SCBI and a weak negative relationship (-0.2-0.03 mm/ $^\circ$C) at Harvard Forest (`r EDF_pheno_Tmax_climwin`).

@@

The raw dendrometer band data were manually inspected before analysis. 
We screened the data for three classes of errors. 
First, when a measurement was drastically different from previous and following measurements, it was assumed to be a human error and removed.
Second, when measurements remained essentially unchanged for several readings, followed by a sudden jump then return to a normal growth pattern, this was assumed to be a case where the band was stuck on the tree bark and then released. 
In these cases, the full annual record for the tree was removed.
Third, data points that deviated substantially from normal growth patterns, but for unknown causes, were removed. 
If a majority of the data points fell into this class within a tree-year, the entire year was removed from the analysis.
We also removed tree-years with small or negligible total growth ($\Delta DBH$ $\le 0.05$ mm; SCBI = 26, Harvard Forest = 253), and tree-years where first intraannual measurement was later than the first spring survey (trees that were missed in the initial census; SCBI = 22, Harvard Forest = 8).
These were removed because they reduce the reliability of predicted growth in the modeled curves.
